---
title: "ch15_html"
author: "Matt & Joshua Wiley"
date: "18 September 2016"
output: html_document
---
```{r echo=FALSE}
##notice the 'echo=FALSE'
##it means the below code will never make it to our knited html
library(data.table)
diris <- as.data.table(iris)
##it is still run, however, so we do have access to it.
```

#This is the top level header; it is not a comment.

This is plain text that is not code.

If we wish *italics*  or **bold** we can easily add those to these documents. Of course, we may need to mention `rmarkdown` is the package used, and inline code is nice for that. If mathematics are requried, then perhaps x~1~^2^ + x~2~^2^ = 1 is wanted. 


##calling out mathematics with a header 2
On the other hand, we may need the mathematics called out explicitly, in which case  $x^{2} + y^{2}= \pi$ is the way to make that happen.

###I like strikeouts, I'm less clear about level 3 headers.
I often find when writing reports that I want to say something is ~~absolutely foolish~~ obviously important to key stakeholders.

######If you ever write something that needs Header 6
Then I believe, as this unordered list suggests:



* You need to embrace less order starting now

    - Have you considered other careers?

```{r echo=FALSE}
summary(diris)
```

However, notice that one can include both the code and the console output:
```{r fig.align="right"}
hist(diris$Sepal.Length)
```
