---
title: "Example Scoring Report"
subtitle: "Item Level Analysis"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout: default
---

# Raw Data

Here is a sample of the data uploaded including the first few and last
rows, and first few and last columns:

```{r echo=FALSE, include = FALSE}
scores <- scores()
scores <- as.data.table(scores)
setnames(scores, 1, "Student")

```

```{r, echo = FALSE, results = 'asis'}
if (nrow(scores) > 6) {
 row.index <- c(1:3, (nrow(scores)-2):nrow(scores))
}

if (ncol(scores) > 6) {
 col.index <- c(1:3, (ncol(scores)-2):ncol(scores))
}

kable(scores[row.index, col.index, with = FALSE])
```

```{r, include = FALSE}
items <- names(scores)[-1]

scores[, SUM := rowSums(scores[, items, with = FALSE])]

## now calculate biserial correlations
## first melt data to be long
scores.long <- melt(scores, id.vars = c("Student", "SUM"))

## calculate biserial correlation, by item
## order from high to low
biserial.results <- scores.long[, .(
  r = round(biserial.cor(SUM, value, level = 2), 3),
  Correct = round(mean(value) * 100, 1)
  ), by = variable][order(r, decreasing = TRUE)]


alpha.results <- cronbach.alpha(scores[, !c("Student", "SUM"), with=FALSE])

rasch.results <- rasch(scores[,!c("Student", "SUM"), with=FALSE])

```

The test overall had `r ifelse(alpha.results$alpha > .6, "acceptable
reliability", "low reliability")` of
alpha = `r format(alpha.results$alpha, FALSE, 2, 2)`.^[Alpha ranges from 0 to 1, with one indicating a perfectly reliable test.]

The graph shows the measurement error by level of
ability.^[Higher values indicate more measurement error, indicating the test is less reliable at very low and very high ability levels (scores).]

```{r, echo = FALSE, fig.width = 5, fig.height = 4}

## The Standard Error of Measurement can be plotted by
vals <- plot(rasch.results, type = "IIC", items = 0, plot = FALSE)
plot(vals[, "z"], 1 / sqrt(vals[, "info"]),
     type = "l", lwd = 2, xlab = "Ability", ylab = "Standard Error",
     main = "Standard Error of Measurement")

```



# Item Analysis

Results for individual items are shown in the following
table.^[*r* indicates the point biserial correlation of an item with the total score. *Correct* indicates the percent of correct responses to a particular item. The items are sorted from highest to lowest correlation.]

```{r, echo = FALSE, results = 'asis'}
kable(biserial.results)
```

